\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Google}{Mountain View, CA}
{Software Engineer}{Oct 2016 -- Present}
\resumeItemListStart
\resumeItem{TensorFlow}
{TensorFlow is an open source software library for numerical computation using data flow graphs; primarily used for training deep learning models. Worked on APIs and performance for training models on Tensor Processing Units (TPU).}
\resumeItem{Apache Beam}
{Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines, as well as a set of language-specific SDKs for constructing pipelines and runners.}
\resumeItemListEnd

% --------Multiple Positions Heading------------
%  \resumeSubSubheading
%   {Software Engineer I}{Oct 2014 -- Sep 2016}
%   \resumeItemListStart
%      \resumeItem{Apache Beam}
%        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%   \resumeItemListEnd

%-------------------------------------------

\resumeSubheading
{Coursera}{Mountain View, CA}
{Senior Software Engineer}{Jan 2014 -- Oct 2016}
\resumeItemListStart
\resumeItem{Notifications}
{Service for sending email, push and in-app notifications. Involved in features such as delivery time optimization, tracking, queuing and A/B testing. Built an internal app to run batch campaigns for marketing etc.}
\resumeItem{Nostos}
{Bulk data processing and injection service from Hadoop to Cassandra and provides a thin REST layer on top for serving offline computed data online.}
\resumeItem{Workflows}
{Dataduct an open source workflow framework to create and manage data pipelines leveraging reusables patterns to expedite developer productivity.}
\resumeItem{Data Collection}
{Designed the internal survey and crowdsourcing platform which allowed for creating various tasks for crowdsourcing or embedding surveys across the Coursera platform.}
\resumeItem{Dev Environment}
{Analytics environment based on Docker and AWS, standardized the Python and R dependencies. Wrote the core libraries that are shared by all data scientists.}
\resumeItem{Data Warehousing}
{Setup, schema design and management of Amazon Redshift. Built an internal app for access to the data using a web interface. Dataduct integration for daily ETL injection into Redshift.}
\resumeItem{Recommendations}
{Core service for all recommendation systems at Coursera, currently used on the homepage and throughout the content discovery process. Worked on both offline training and online serving.}
\resumeItem{Content Discovery}
{Improved content discovery by building a new onboarding experience on coursera. Used this to personalize the search and browse experience. Also worked on ranking and indexing improvements.}
\resumeItem{Course Dashboards}
{Instructor dashboards and learner surveying tools, which helped instructors run their class better by providing data on Assignments and Learner Activity.}
\resumeItemListEnd

\resumeSubHeadingListEnd
