

\documentclass[letterpaper,10pt]{moderncv}      
\usepackage[english]{babel}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Prateek}{Nigam}


\phone[mobile]{+353892248792}               
\email{nigamprateek38@gmail.com}                             


\begin{document}

\recipient{To}{Tenth Revolution Group}
\date{\today}
\opening{Hi!}
\closing{Thanks in advance!}
\enclosure[Attachment]{CV}
\makelettertitle

I'd like to express my interest in the AI Engineer contract role. I have a little over five years of experience building and deploying AI/ML systems on AWS, and your focus on practical, production-grade generative AI solutions really resonates with me.

At Fractal, I've worked closely with Fortune 500 clients, helping take models from prototype to production on AWS services such as SageMaker, Lambda, ECR, S3, and API Gateway. I'm used to small, focused teams and iterating based on real customer feedback, which is the kind of environment I enjoy and learn the most from.

More recently, I've been developing generative AI and multi-agent workflows with LangChain/LangGraph and RAG pipelines, integrating LLMs with serverless components and thinking carefully about evaluation and guardrails for safe use in production. I'm also interested in growing my skills with AWS CDK and TypeScript as part of your stack.

I would be grateful for the opportunity to discuss how my experience could be useful to your team and your customers.

\vspace{0.5cm}
Thanks in advance!

\vspace{0.5cm}
Best regards, \\

\textbf{Prateek Nigam} \\
\href{https://prateeknigam.dev/}{https://prateeknigam.dev}\\


\end{document}
