\section{Experience}
 \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://drive.google.com/file/d/10sMPuoBGO8S7p0PfTe7Hr_CULP5aWhup/view}{Fractal Analytics}}{Mumbai, India}
      {\textcolor{Blue}{ML Engineer}}{Oct 2021 -- Aug 2024}
      
      \resumeItemListStart
        \resumeItem{Technical Subject-Matter Expert}
          {Owned technical delivery and stakeholder communications for \textbf{three Fortune-500 CPG accounts}, translating complex model outputs into actionable marketing investment decisions.}

        \resumeItem{ML Model Deployment on AWS}
          {Designed and deployed a production ML inference pipeline on AWS, dockerizing hierarchical Bayesian models (Pyro/NumPyro) and orchestrating SageMaker batch transform jobs integrated with S3. Exposed ML-backed inference endpoints via production APIs, operating them with \textbf{CI/CD, monitoring, and incident-aware design}, reducing manual processing by \textbf{40\%} and enabling a projected \textbf{5–10\% ROI} improvement for CPG clients.}         
          
        \resumeItem{Model Performance Optimization}
          {Re-architected ML model codebase by refactoring legacy Theano implementation to JAX/NumPyro, applying efficient array operations and algorithmic optimizations to reduce runtime from \textbf{5 hours to 8 minutes (37x improvement)} and thus enabled 50\% higher project throughput and capacity for 10x larger datasets while maintaining clean, maintainable code and automated monitoring to ensure model reliability and governance.}
          
        \resumeItem{End-to-End Feature Ownership}
          {Owned end-to-end development of granular targeting ML system from design through deployment: built LGBM classification models at zip-code level (\textbf{70\% accuracy}), developed feature engineering pipelines processing geographic and demographic data, and delivered production-ready solution.}
                  
        \resumeItem{MLOps \& CI/CD Implementation}
          {Standardized MLOps deployment patterns ensuring reproducibility across environments and collaborated with DevOps teams to implement CI/CD pipelines for model deployment workflows.}

        % \resumeItem{Agile Collaboration \& Stakeholder Alignment}
        %   {Developed regression and decision tree models for KPI attribution, collaborating with client stakeholders in iterative Agile sprints to integrate business insights, achieving 48\% F1 score.}

          

      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://drive.google.com/file/d/1n0uYAw9foyXEYLjLYKpWT3szMy8oMVQK/view}{Capgemini India Pvt Ltd.}}{Bangalore, India}
      {\textcolor{Blue}{Software Engineer}}{Aug 2019 -- Oct 2021}
      \resumeItemListStart
        \resumeItem{Scalable Data Pipelines}
          {Enhanced PySpark ETL tools for large-scale data processing, improving efficiency by 30\% and establishing data foundations for downstream ML pipelines}
      
        \resumeItem{Enterprise Security \& Integration}
        {Implemented enterprise SSO (Kerberos + LDAP) for Active Directory integration, ensuring secure data access and security compliance across platforms.}
        
      \resumeItemListEnd
   
  \resumeSubHeadingListEnd